\documentclass[10pt]{article}

\usepackage[left=1in, right=1in, top=0.5in, bottom=0.5in]{geometry}
\usepackage[unicode,
            pdfencoding=auto,
            pdfinfo={
              Title={stephenmcgruer/resume},
              Author={Stephen McGruer},
              Subject={Stephen McGruer Résumé},
              Keywords={}
            },
            ]{hyperref}
\usepackage{libertine}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage[absolute]{textpos}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xltxtra}
\usepackage{xspace}

% Include the generic setup/commands/etc.
\include{misc}

\begin{document}
\pagestyle{empty}

%%%%% Title. %%%%%%

\par{\centering {\Huge Stephen \textsc{McGruer} }\bigskip\par}

%%%%% Contact information. %%%%%%

\section{Contact Details}

\begin{multicols}{2}
\setlength{\parskip}{0pt}

\begin{tabularx}{\linewidth}{l X}
  \textsc{email}       & \href{mailto:stephen.mcgruer@gmail.com}{stephen.mcgruer@gmail.com} \\
\end{tabularx}

\vfill
\columnbreak

\begin{tabularx}{\linewidth}{l X}
  \textsc{Website}     & \href{http://www.stephenmcgruer.com/}{stephenmcgruer.com} \\
\end{tabularx}

\end{multicols}

%%%%% Education. %%%%%%

\section{Education}
\vspace{0.25em}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}r l p{5.5cm} r}
  \degree{Jul 2013}%
  {M.Inf (Hons. First Class)}%
  {Informatics}%
  {University of Edinburgh}
\end{tabular*}

%%%%% Work Experience. %%%%%%

\vspace{1em}
\section{Experience}

\setlength\LTleft{0pt}
\setlength\LTright{0pt}
\vspace{-0.25em}

\begin{longtable}{@{\extracolsep{\fill}} l | l r}

  \experience{12/16 - Current}%
    {Senior Software Engineer}%
    {at}%
    {Google Canada}%
    {Senior Software Engineer on the Google Chrome team. Currently Tech Lead /
     Manager of the Web Payments team, leading a team of 3 engineers focused
     on improving payment experiences on the web from e-commerce to alternative
     monetization efforts. Previously worked on Web Interoperability and Animations.}

  \experience{05/16 - 11/16}%
    {Senior Software Engineer}%
    {at}%
    {Google Canada}%
    {Technical Lead of the Google Fiber Content Playback team. Leading a team of 7
     engineers supporting content playback across three ecosystems; an embedded
     set-top box providing the main TV experience, and both iOS and Android apps
     providing a mobile experience for Fiber TV customers.}

  \experience{10/13 - 04/16}%
    {Software Engineer}%
    {at}%
    {Google Canada}%
    {Software developer in the \href{https://fiber.google.com/about/}{Google Fiber}
     TV team. Working on Google Fiber set-top box, including \skill{HLS} based
     set-top to mobile device streaming, \skill{verified boot} of an embedded
     system, and support for mobile device screen sharing via
     \href{http://www.wi-fi.org/wi-fi-ce}{Miracast}.}

  \experience{06/12 - 09/12}%
    {Software Engineering Intern}%
    {at}%
    {Google Mountain View}%
    {Software developer in the Google Web Search team, maintaining and
     developing the \skill{Google Search} backend. Adapted the
     \href{https://www.eclipse.org/mat/}{Eclipse Memory Analyzer} for automated
     memory usage monitoring of a large-scale embedded JVM, and reduced memory
     inefficiencies in a \java/\cpp \jni interface. Also tutored students in the
     \href{https://www.google.com/edu/programs/computer-science-summer-institute-cssi/}{Google CSSI program},
     helping them with \python, \skill{Google App Engine}, and project design
     and management.}

  \experience{06/11 - 09/11}%
    {Software Engineering Intern}%
    {at}%
    {Google London}%
    {Software developer in the Android Marketplace Publisher Website\footnote{Now
     Google Play Developer Console} team. Working with the \skill{Google Web Toolkit}
     and \skill{Google Chart Tools}, increased the visibility of Android app
     crashes to developers. Refactored large amounts of existing code to follow
     a Model-View-Presenter design.}

  \experience{06/10 - 09/10}%
    {Software Engineering Intern}%
    {at}%
    {Thales Optronics UK}%
    {Working on an in-house resource management application, created a \jsp
     interface between a \php webpage and a
     \href{https://www.jboss.org/drools/}{JBoss Drools} business rules engine
     to allow non-technical employees to easily define complex
     resource-management requirements and processes.}

\end{longtable}

%%%%% Skills/Languages %%%%%%

\vspace{-1em}
\section{Skills \& Languages}

\begin{multicols}{3}
\raggedcolumns

\begin{itemize}

% Remove the normal bullet points.
\renewcommand{\labelitemi}{}

% Don't bold skill names here.
\renewcommand{\skill}{\textnormal}

% Cluster things a bit closer.
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\skills{\bash}{\twoskill}
\skills{\ccpp}{\threeskill}
\skills{\git}{\twoskill}
\skills{GNU/\linux}{\twoskill}
\skills{\java}{\twoskill}
\skills{\js}{\oneskill}
\skills{\python}{\twoskill}

\end{itemize}

\end{multicols}
\vspace{-1em}
  \begin{footnotesize}
    \oneskill Small-scale projects and/or assignments \hfill 
    \twoskill Multiple projects and/or experience teaching \hfill
    \threeskill Large-scale and/or multi-group projects
  \end{footnotesize}

%%%%% Honors/Awards %%%%%%

\vspace{0.75em}
\section{Honors/Awards}
\vspace{0.25em}
\begin{tabularx}{\textwidth}{r|X}
2013 & Master of Informatics, Class Medal \\
2013 & UCL CREST Final Year Computer Science Project Competition (Finalist) \\
2011 & Netcraft Prize for Top 6 Penultimate Year Students \\
\end{tabularx}

%%%%% Activities. %%%%%%

\vspace{0.75em}
\section{Activities}
\vspace{0.25em}
running, baking, \href{https://github.com/stephenmcgruer}{programming}, boardgaming, gaming

%%%%% Footnote. %%%%%%

\null\vfill
\footnotesize{
  Online:  \href{http://www.stephenmcgruer.com/resume.pdf}{stephenmcgruer.com/resume.pdf} \hfill
  Source:  \href{https://github.com/stephenmcgruer/resume}{github.com/stephenmcgruer/resume}
}

\end{document}
